---
title: "Loan_EDLD629_HW3"
author: "Christopher Loan"
date: "5/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lme4)
library(brms)
```

```{r}
dat <- 
  rio::import(here::here('Data', 'thai-education.csv')) %>% 
  mutate(
    repeated_grade_num = 
      if_else(repeated_grade == 'no', 0, 1))
```

## Main question: 

`Does the relation between students' coded sex and likelihood of repeating depend upon the mean SES at the school level?`

```{r}
mod1 <- brm(
    data = dat, 
    formula = 
      repeated_grade_num ~ sex*msesc + (sex | schoolid),
    family = bernoulli(link = 'logit'), 
    cores = 4,
    backend = "cmdstan"
    )
```

```{r}
summary(mod1)
```

It appears that the relation between students' coded sex and likelihood of repeating does not depend upon the mean SES at the school level. We see this with the 95% credible intervals of the interaction including 0.

## The Rest

**1. To what extent does the likelihood of repeating a grade vary between schools?**

The likelihood of repeating a grade varies between schools with a standard deviation in log-odds of 1.42 (95% CIs = [1.23, 1.62])

**2. Does the coded sex of the student relate to this likelihood?**

Yes, girls were less likely to repeat a grade than boys, with an average log-odds difference of -0.46 (95% CIs = [-0.66, -0.25]), and a standard deviation of 0.36 ([0.04, 0.68]).

**3. Does the relation between students' coded sex and likelihood of repeating depend upon the school in which they are enrolled?**

Yes, the standard deviation in slope of sex was 0.36 ([0.04, 0.68]). 


